---
title: "ccxt quatro"
subtitle: "Until now!"
format: html
editor: source
execute:
  echo: false
---

```{r setup, include=FALSE}
# str(knitr::opts_chunk$get())
knitr::opts_chunk$set(echo = TRUE, tidy = "styler",
  warning = FALSE, message = FALSE, echo = FALSE,
  fig.path = "./inst/pngs/"
)
pacman::p_load(targets, dplyr, stringr)

targets::tar_config_set(store = 
  # _targets in ./inst to pass R CMD check
  # WARNING: relative to Rmd vignette directory.
    # see ./_targets.yaml to move _targets folder inside ./inst/
    here::here('inst', '_targets')
  )
targets::tar_config_get("store") # "_targets"
```

## info
### ccxt 
```{r ccxt_info}
tar_read(ccxt_info)
```


## FTX
```{r ftx_info}
tar_read(ftx_info)
```


## FTX markets
```{r ftx_markets}
top_of_list <- function(x) str(x, max.level = 1, list.len = 4)
tar_read(ftx_markets) %>% top_of_list()
```

## ftx properties
```{r ftx_has}
tar_load(ftx_has)
ftx_has %>% top_of_list()
# https://github.com/ccxt/ccxt/wiki/Manual#exchange-time
```

## ftx tickers
```{r tickers_ftx}
tar_load(tickers_ftx) %>% top_of_list()
tar_load(inpp)
```

## FTX ticker info
+ Parameters
  + pairs: `r inpp$pairs`
  + origin = `r inpp$origin`
  + timeframe = `r inpp$timeframe`, 
  + limit = `r inpp$limit`

Sample info for dex aggregators on solana. 
```{r tickers_info}
tar_load(tickers_info) 
# solana coins for dex aggregators
coins_sol <- c(Orca = 'ORCA', Raydium = 'RAY', Mango = 'MNGO')
tickers_info %>% 
  filter(symbol %>% str_detect(paste(coins_sol, collapse='|'))) %>% 
  glimpse()
```

```{r tickers_not_info}
tar_read(tickers_not_info)
tar_read(future_spot_tbl)
```


## FTX ohlcv snapshots

```{r ftx_ohlcv_snapshots}
tar_read(ftx_ohlcv_snapshots)
```


# Alternative exchanges
Alternative exchanges are available.
## tickers_binance
```{r tickers_binance}
tar_read(tickers_binance)  %>% top_of_list()
# columns vary by exchange - binance offers more info than most
tar_read(tickers_not_info_binance) %>% 
  filter(symbol %>% str_detect(paste(coins_sol, collapse='|'))) %>% 
  glimpse()
```


# Appendix

## TODOs  
+ retrieve the symbols available for trading in an exchange
  + e.g. Star Atlas (ATLAS & POLIS), Oxigen (OXY), Orca (ORCA), Raydium (RAY), Mango Markets (MNGO)
  + https://azcoinnews.com/top-crypto-strategist-names-5-solana-projects-with-massive-growth.html
    + Bitgert (BRISE), Helium (HNT), Monero (XMR), Fantom (FTM), Avalanche (AVAX), 
    + https://www.analyticsinsight.net/avalanche-avax-fantom-ftm-helium-hnt-bitgert-brise-monero-xmr-the-best-crypto-for-2022/

## Render
```{r browseURL, eval = FALSE}
# library(rmarkdown)
# render("intro.Rmd")
browseURL("intro.html")
# dependency graph 
tar_visnetwork() 
```