---
title: "ccxt README"
# subtitle: "Until now!"
editor: source
execute:
  echo: false
format: markdown_github
# output:
#   github_document:
# output: rmarkdown::html_vignette
vignette: >
  %\VignetteEngine{knitr::knitr}
  %\VignetteIndexEntry{Title of your vignette}
  %\usepackage[UTF-8]{inputenc}
---

<!-- README.md is generated from README.qmd. 
  Please edit that file. 
-->

```{r, include = FALSE}
knitr::opts_chunk$set(
  echo = TRUE, 
  warning = FALSE, 
  message = FALSE, 
  tidy = "styler",
  collapse = TRUE,
  comment = "#>",
  fig.path = c("./inst/pngs/", 
    "man/figures/README-")[1],
  out.width = "100%"
)
# str(knitr::opts_chunk$get())
```
```{r setup targets, include=FALSE}
pacman::p_load(targets, dplyr, stringr)

targets::tar_config_set(store = 
  # _targets in ./inst to pass R CMD check
  # WARNING: relative to Rmd vignette directory.
    # see ./_targets.yaml to move _targets folder inside ./inst/
    here::here('inst', '_targets')
  )
targets::tar_config_get("store") # "_targets"
```

![Visualization of this repo](./diagram.svg)

+ using the [repo-visualizer](https://github.com/githubocto/repo-visualizer) GitHub Action
+ [diagram.yml](/.github/workflows/diagram.yml). 
  + excluding `ignore` and `.github` folders, via `excluded_paths` config.


# `ccxt` goals

<!-- badges: start -->

<!-- badges: end -->

-   \(H\) OHLCV snapshots from FTX, Binance and Coinbase.

-   \(M\)

-   \(L\) FTX perpetuals

## Installation

<!-- You can install the released version of ccxt from [CRAN](https://CRAN.R-project.org) with: 
``` r
install.packages("ccxt")
```
-->

-   Development version from [GitHub](https://github.com/JohnGavin/ccxt):

``` r
if (!require(devtools)) install.packages("devtools")
devtools::install_github("JohnGavin/ccxt")
```

## Example

```{r example}
library(ccxt)
## basic example code
```

```{r ccxt_info, echo = TRUE}
#| label: ccxt_info
tar_read(ccxt_info)
```
Information on each coin listed on FTX.
```{r tickers_not_info, echo = FALSE}
tar_read(tickers_not_info)
```

### TODOs

-   render `README.Rmd`
    -   `devtools::build_readme()`
-   GitHub Actions to re-render `README.Rmd` every time you push.
    -   See <https://github.com/r-lib/actions/tree/master/examples>
    -   e.g. commit and push to see the updated plots

```{r ohlcv, echo = FALSE}
# ./ccxt/man/figures via fig.path = "man/figures/README-",
# plot(ohlcv)
```

## References
